### 2019-12-17 ic-journal/sos.tex
Changed most "w.r.t." to "with respect to"; removed "the" from (of the type ...) following other papers.

The CCS formalisation starts with type definitions for action,
relabeling and then the  processes. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
to $\mathscr{L}$ (the set of names for labels) mentioned at the beginning
of Section~\ref{ss:ccs}. (Thus the
cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' depends on its type variable:
when $\beta$ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is countable.)
All labels are divided into input and output ones.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
following syntax:
\begin{lstlisting}
Datatype: Label = name 'b | coname 'b
End
\end{lstlisting}
Intuitively, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' turns names in $\mathscr{L}$ into \emph{input and output labels}.
For instance, if the type $\beta$ is instantiated to \texttt{string}
(the type of all ASCII strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input \emph{label} $a$ and output
\emph{label} $\overline{b}$, respectively.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
union of all visible actions (input and output labels) and the invisible action $\tau$
(\texttt{tau}). For instace, the input \emph{action} $a$ and output
\emph{action} $\overline{b}$ of the type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively. On the
other hand, \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions of the type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
\HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.

The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for all CCS terms,
has two type variables $\alpha$ and $\beta$ corresponding
to the set of agent variables $\mathscr{X}$
and the set of names $\mathscr{L}$,
respectively. (Indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
w.r.t. the choice of these two sets.)
%
The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is defined inductively by the
\texttt{Datatype} package
(here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
  functions; we have also formalised relabeling, though it is not
  discussed below):
\begin{lstlisting}
Datatype: CCS = nil
              | var 'a
              | prefix ('b Action) CCS
              | sum CCS CCS
              | par CCS CCS
              | restr (('b Label) set) CCS
              | relab CCS ('b Relabeling)
              | rec 'a CCS
End
\end{lstlisting}
The above definition allows us to write terms like \texttt{nil} and
\texttt{sum P Q} in HOL4. Their correspondences with conventional CCS notations
in the literature are given in Table~\ref{tab:ccsoperator}, where
most CCS operators have also more readable abbreviated forms,
either for end users or for \TeX{} outputs. (All
  formal theorems and definitions in this paper
  are generated from HOL4. Also, by default, all theorems are fully
  specialised with outermost universal quantifiers removed.)

@@

A successful invocation of the definitional principle returns three
important theorems (\texttt{TRANS_rules}, \texttt{TRANS_ind} and \texttt{TRANS_cases}):

@@

  \item \texttt{TRANS_rules} is a conjunction of implications (each

@@

    extracted from the \emph{rules} theorem:

@@

\item \texttt{TRANS_ind} is the induction principle for the relation

@@

\item \texttt{TRANS_cases} is the so-called `cases' or `inversion' theorem for

>>>>

The CCS formalisation starts with type definitions for action,
relabeling and then the  processes. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
to $\mathscr{L}$ (the set of names for labels) mentioned at the beginning
of Section~\ref{ss:ccs}. (Thus the
cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' depends on its type variable:
when $\beta$ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is countable.)
All labels are divided into input and output ones.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
following syntax:
\begin{lstlisting}
Datatype: Label = name 'b | coname 'b
End
\end{lstlisting}
Intuitively, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' turns names in $\mathscr{L}$ into \emph{input and output labels}.
For instance, if the type $\beta$ is instantiated to \texttt{string}
(the type of all ASCII strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input \emph{label} $a$ and output
\emph{label} $\overline{b}$, respectively.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
union of all visible actions (input and output labels) and the invisible action $\tau$
(\texttt{tau}). For instace, the input \emph{action} $a$ and output
\emph{action} $\overline{b}$ \hl{of type} ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively. On the
other hand, \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions \hl{of type} ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
\HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.

The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for all CCS terms,
has two type variables $\alpha$ and $\beta$ corresponding
to the set of agent variables $\mathscr{X}$
and the set of names $\mathscr{L}$,
respectively. (Indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
\hl{with respect to} the choice of these two sets.)
%
The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is defined inductively by the
\texttt{Datatype} package
(here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
  functions; we have also formalised relabeling, though it is not
  discussed below):
\begin{lstlisting}
Datatype: CCS = nil
              | var 'a
              | prefix ('b Action) CCS
              | sum CCS CCS
              | par CCS CCS
              | restr (('b Label) set) CCS
              | relab CCS ('b Relabeling)
              | rec 'a CCS
End
\end{lstlisting}
The above definition allows us to write terms like \texttt{nil} and
\texttt{sum P Q} in HOL4. Their correspondences with conventional CCS notations
in the literature are given in Table~\ref{tab:ccsoperator}, where
most CCS operators have also more readable abbreviated forms,
either for end users or for \TeX{} outputs. (All
  formal theorems and definitions in this paper
  are generated from HOL4. Also, by default, all theorems are fully
  specialised with outermost universal quantifiers removed.)

@@

\hl{The} successful invocation of the definitional principle returns three
important theorems \hl{(\texttt{TRANS_rules}, \texttt{TRANS_ind} and \texttt{TRANS_cases})}:

@@

  \item \hl{\texttt{TRANS_rules}} is a conjunction of implications (each

@@

    extracted from \hl{\texttt{TRANS_rules}}:

@@

\item \hl{\texttt{TRANS_ind}} is the induction principle for the relation

@@

\item \hl{\texttt{TRANS_cases}} is the so-called `cases' or `inversion' theorem for
